Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-13 conclusions.tex
Added mention of signal based vetoes
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1069 ccdd05d5-56c1-461a-bf98-85f6876523b4
Slight rewording
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1070 ccdd05d5-56c1-461a-bf98-85f6876523b4
Moved composite detection statistic into future work section
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1071 ccdd05d5-56c1-461a-bf98-85f6876523b4

We have demonstrated a computationally feasible procedure for the rapid and
even early-warning detection of \GW{}s emitted during the coalescence
of neutron stars and stellar-mass black holes. Our method is as fast as
standard \fft{} convolutions but allows for latency-free, real-time
operation.  We anticipate requiring $\sim 4 \times 10 = 40$ modern multi-core computers to
search for binary neutron stars using coincident \GW\ data from a four-detector network.
This is well within the current computing capabilities of the \LIGO{} Data Grid%
\footnote{\url{https://www.lsc-group.phys.uwm.edu/lscdatagrid/}}. In the future, this
could be improved upon further by conditionally reconstructing the \SNR{} time-series
only during times when a composite detection statistic crosses a
threshold~\citep{svd-compdetstat}.

@@

Although we have demonstrated a feasible method for advance detection we have
not yet explored triggering, coincidence, and ranking of gravitational wave
candidates in a framework that supports early \EM\ followup.  If adjacent time slices
have non-negligible cross-correlation with each other, then there may be some
subtleties in the design of these postprocessing stages that we must address in order
to translate the early-warning outputs into candidate events.

>>>>

We have demonstrated a computationally feasible procedure for the rapid and
even early-warning detection of \GW{}s emitted during the coalescence
of neutron stars and stellar-mass black holes. Our method is as fast as
standard \fft{} convolutions but allows for latency-free, real-time
operation.  We anticipate requiring $\sim 4 \times 10 = 40$ modern multi-core computers to
search for binary neutron stars using coincident \GW\ data from a four-detector network.
This is well within the current computing capabilities of the \LIGO{} Data Grid%
\footnote{\url{https://www.lsc-group.phys.uwm.edu/lscdatagrid/}}.

@@

% This passage goes in the 'future work' part, but I am having trouble working it in.
\begin{comment}
In the future, this
could be improved upon further by conditionally reconstructing the \SNR{} time-series
only during times when a composite detection statistic crosses a
threshold~\citep{svd-compdetstat}.
\end{comment}

Although we have demonstrated a feasible method for advance detection we have
not yet explored triggering, coincidence, and ranking of gravitational wave
candidates in a framework that supports early \EM\ followup.  If adjacent time slices
have non-negligible cross-correlation with each other, then there may be some
subtleties in the design of these postprocessing stages that we must address in order
to translate the early-warning outputs into candidate events.  The time-slice
decomposition and the \SVD\ will help us form low-latency signal based vetoes
(for example, a $\chi^2$ statistic) that will help us here.
